% 摘要
\begin{cnabstract}
	\songti \zihao{-4}
	\absemph{目的：}
	本文建立多个基于$SIR$的衍生病毒传播模型，
	并使用新型冠状病毒肺炎（COVID-19）疫情的官方发布数据来对这些模型进行拟合，
	在所建立的模型中找出一个与该疫情拟合度最高的病毒传播模型。
	并根据最优模型对该病毒传播进行更深一步的分析。
	\absemph{方法：}
	基于$SIR$病毒传播模型，
	根据病毒特点一步步迭代构建新的预测模型（
	考虑潜伏人群得到$SEIR$模型、
	考虑死亡人群得到$SEIRD$模型、
	考虑复阳人群得到$SEIRS$模型）。
	并基于官方公布的数据进行拟合，
	根据拟合效果选择最优模型，
	从使用最优模型的最佳估计参数中提取有效信息。
	\absemph{结果：}
	在提出的四个模型($SIR$、$SEIR$、$SEIRD$、$SEIRS$)中，
	通过对比模型与实际数据的拟合程度优劣，
	判断$SEIRD$模型最符合疫情传播趋势，
	并通过分析$SEIRD$模型的最优估计参数来计算病毒的基本生殖数$R_0$，
	基本生殖数$R_0$代表了病毒的有效传播速率，
	$R_0$越低代表病毒传播速率越低。
	计算出整个疫情期间的$R_0=1.754$，
	所得$R_0$值符合官方发布数据$1.4\leq R_0\leq 3.8$及众多文献的结论。
	并通过数据分段拟合计算出疫情的初期(未隔离甚至人口密集状态下)$R_0=5.937$，
	以及疫情后期(隔离措施到位)$R_0=1.081$，
	所得疫情前期$R_0$符合相关文献所得结论$4.16\leq R_0\leq 7.10$，
	说明该模型可以较为准确的描述疫情传播过程，
	可用于类似传染病的预测。
	\\
	\absemph{关键字：} SEIR， 数学模型，传染病， COVID-19
\end{cnabstract}
\begin{enabstract}
	\zihao{-4}
	\absemph{Target:}
	This article establishes multiple $ SIR $ derived virus propagation models,
	and use the officially released data of the new coronavirus pneumonia (COVID-19) epidemic situation to fit these models,
	Find a virus transmission model with the best fit to the epidemic in the established model.
	And according to the optimal model for further analysis of the spread of the virus.
	\absemph{Method:}
	Based on the $ SIR $ virus propagation model,
	according to the characteristics of the virus, iteratively build a new prediction model step by step (
	consider the latent crowd to get the $ SEIR $ model,
	consider the death crowd get $ SEIRD $ model,
	consider the Fuyang crowd to get the $ SEIRS $ model).
	and based on the official data, fitting
	choose the best model according to the fitting effect,
	extract effective information from the best estimated parameters using the optimal model.
	\absemph{Result:}
	Among the four models proposed ($ SIR $, $ SEIR $, $ SEIRD $, $ SEIRS $),
	compare the fit of the model and the actual data,
	judging that the $ SEIRD $ model is most in line with the spreading trend of the epidemic,
	and by analyzing the optimal estimated parameters of the $ SEIRD $ model to calculate the basic reproduction number of the virus $ R_0 $,
	the basic reproduction number $ R_0 $ represents the effective transmission rate of the virus,
	the lower the $ R_0 $, the lower the virus transmission rate.
	Calculate $ R_0 = 1.754 $ for the entire epidemic period,
	the obtained $ R_0 $ value is in accordance with the official release data $ 1.4 \leq R_0 \leq 3.8 $ and the conclusions of many literatures.
	and calculate the early stage of the epidemic through data segmentation fitting (unisolated or even densely populated) $ R_0 = 5.937 $
	and later in the outbreak (quarantine measures are in place) $ R_0 = 1.081 $,
	earlier outbreaks of $ R_0 $ in line with conclusions from relevant literature $ 4.16 \leq R_0 \leq 7.10 $,
	it shows that the model can describe the epidemic transmission process more accurately,
	it can be used to predict similar infectious diseases.
	\\
	\absemph{Key Words:} SEIR, mathematical model, epidemic, COVID-19
\end{enabstract}